\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-10 paper/ms.tex
got rid of useless sentence
Update from seed 0 runs
Cite Robert

\subsection{Log-likelihood}
The log-likelihood code is standard:
\begin{CodeChunk}
\begin{CodeInput}
double StraightLine::log_likelihood() const
{
    // Grab the dataset
    const std::vector<double>& x = Data::get_instance().get_x();
    const std::vector<double>& y = Data::get_instance().get_y();

@@

\subsection{Mixture model results}
The data and the posterior mean fit are shown
in Figure~\ref{fig:galaxies} and the posterior distribution for
$N$ is shown in Figure~\ref{fig:galaxies_N}.

@@

\subsection{ABC with Nested Sampling}
NS can be used for ABC by noting that Equation~\ref{eqn:abc_posterior}
is of the same form as a constrained prior, only instead of being the prior
for the parameters $p(\theta | M)$ defined on the parameter space, it is
the {\em joint prior} for the parameters and the data,
$p(\theta, D |M) = p(\theta | M)p(D | \theta, M)$, defined on the product
space of possible parameters and datasets. Therefore, to implement
ABC in \pkg{DNest4}, you implement a model class
whose \code{from\_prior} member function generates parameters {\em and simulated
data} from the joint prior, and whose \code{perturb} member function
proposes changes to the parameters and/or the simulated data, in a
manner consistent with the joint prior. The \code{log\_likelihood} function
of the class, instead of actually evaluating the log likelihood, should
evaluate $-\rho(D; D_{\rm observed})$. Then, running the sampler
will create levels which systematically decrease $\rho$. The samples from
a particular level then represent the ABC posterior defined in
Equation~\ref{eqn:abc_posterior} with $\epsilon$ corresponding to minus
the ``log likelihood'' of the level.
A single \pkg{DNest4} run allows you to test sensitivity
to the value of $\epsilon$ using a single run.

@@

>>>>

\subsection{Log-likelihood}
The log-likelihood for the model is evaluated and returned by the
\code{log\_likelihood} member function. For the straight line
fitting example, the log likelihood is based on the
normal density, and the code is given below.
\begin{CodeChunk}
\begin{CodeInput}
double StraightLine::log_likelihood() const
{
    // Grab the dataset
    const std::vector<double>& x = Data::get_instance().get_x();
    const std::vector<double>& y = Data::get_instance().get_y();

@@

\subsection{Mixture model results}
The data and the posterior mean fit are shown
in Figure~\ref{fig:galaxies} and the posterior distribution for
$N$ is shown in Figure~\ref{fig:galaxies_N}.
The marginal likelihood was $\ln(Z) = -242.2$, and
the information (measured in nats) was $\mathcal{H} = 32.3$.

@@

\subsection{ABC with Nested Sampling}
NS can be used for ABC by noting that Equation~\ref{eqn:abc_posterior}
is of the same form as a constrained prior, only instead of being the prior
for the parameters $p(\theta | M)$ defined on the parameter space, it is
the {\em joint prior} for the parameters and the data,
$p(\theta, D |M) = p(\theta | M)p(D | \theta, M)$, defined on the product
space of possible parameters and datasets. Therefore, to implement
ABC in \pkg{DNest4}, you implement a model class
whose \code{from\_prior} member function generates parameters {\em and simulated
data} from the joint prior, and whose \code{perturb} member function
proposes changes to the parameters and/or the simulated data, in a
manner consistent with the joint prior. The \code{log\_likelihood} function
of the class, instead of actually evaluating the log likelihood, should
evaluate $-\rho(D; D_{\rm observed})$. Then, running the sampler
will create levels which systematically decrease $\rho$. The samples from
a particular level then represent the ABC posterior defined in
Equation~\ref{eqn:abc_posterior} with $\epsilon$ corresponding to minus
the ``log likelihood'' of the level.
A single \pkg{DNest4} run allows you to test sensitivity
to the value of $\epsilon$ using a single run.
The marginal likelihood reported will be
the probability that $\rho\left(D; D_{\rm observed}\right) < \epsilon$
given the model, although caution should be applied if
using this for model selection \citep{robert}.

@@

\bibitem[Robert et al.(2011)]{robert}
Robert, C.P., Cornuet, J.M., Marin, J.M. and Pillai, N.S., 2011. Lack of confidence in approximate Bayesian computation model choice. Proceedings of the National Academy of Sciences, 108(37), pp.15112-15117.
